%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\usepackage{fontawesome}
\usepackage{setspace}
\usepackage{hyperref}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Gahan Saraiya} % Your name
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{ 
  \faPhone \ +91 7359508173 \\
  \faEnvelope \ \href{mailto: gahansaraiya@gmail.com}{gahansaraiya@gmail.com} \\  
  \faLinkedin \ \href{https://www.linkedin.com/in/gahan-saraiya/}{linkedin.com/in/gahan-saraiya} \\ \faGithub \   \href{https://github.com/gahan9/}{github.com/gahan9} 
}  % Your phone number and email

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
    pdfpagemode=FullScreen,
    }
\begin{document}

% AI/ML - 0
% DevOps - 1
% PhD - 2
\def\profile{0}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}
{Senior System Software \& Firmware Engineer specializing in \textbf{UEFI firmware}, \textbf{EDK2}, \textbf{OpenBMC}, and platform enablement. 9+ years experience in firmware bring-up, \textbf{Open Source} contributions (\textbf{Mantis database}), \textbf{RAS} (Reliability, Availability, Serviceability), and \textbf{GPU firmware}. Actively engaged in upstream-first development, seeking to architect and optimize next-generation high-performance server platforms.}

\end{rSection}




%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{SOFTWARE TOOLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{4ex}} l }

% PROFILE 0
\if\profile0
Languages & UEFI \textbf{C}, \textbf{C++}, \textbf{Python}, Shell, SQL, LaTeX, YAML 
\\
Firmware/BMC & \textbf{UEFI}, \textbf{EDK2}, \textbf{OpenBMC}, Yocto, PLDM, IPMI, \textbf{Redfish}, \textbf{fwupd}, Secure Boot, TPM
\\
Platform & Systemd, device tree, bootloaders, kernel/driver debug, SoC bring-up
\\
RAS & \textbf{RAS for GPU firmware}, \textbf{Mantis Database}, \textbf{ROCm}, SEL/CPER, telemetry
\\
I/O & I2C/SMBus, SPI, UART, JTAG, Ethernet, CPLD/FPGA hooks
\\
Build/CI & Yocto, CMake, Git, Jenkins, GitHub Actions, Docker/OCI, Terraform
\\
\fi

%  PROFILE 1
\if\profile1
Languages & Python, Shell Scripting, SQL, LaTeX, YAML 
\\
Frameworks & Pytorch, Pytest, Edk2, PyCUDA, Pandas, UEFI, Selenium, Redfish
\\
Architecture Design & Parallel Programming System Architecture, ROCm, HIP Programming
\\
Tools and Services & GitHub Actions, Jenkins, Restful APIs, Teamcity, Terraform,
\\ & Docker, Docker Compose, Jenkins, TeamCity, GiT 
\\
Cloud Technologies & AWS EC2, AWS S3, AWS Cloudwatch, VPC Networking, AWS Sage Maker, 
\\ & AWS Lambda, AWS Cloudfront, ECR, ECS, EKS, JFrog Artifactory
\\ & GCP, Azure, Digital Ocean
    
\fi

\end{tabular}

\end{rSection}


%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	Experience SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

{\bf Senior System Software Designer at AMD India Pvt Ltd} \hfill {Mar 2024 - Present }
\begin{itemize}
\if\profile1
    \item Workload execution pool management for cross geo platforms for CI/CD on Jenkins
    \item Release management of ROCm builds for production, non-production and various other categories with matrix of configuration of OS and toolchain
    \item Docker orchestration on enterprise registry
    \item Platform provisioning migration with terraform
\fi
    \item Drive \textbf{RAS for GPU firmware with use-case scenario injection} on \textbf{ROCm} for MI2XX/MI3XX SKUs; define reliability/availability criteria for data center SKUs.
    \item Architect in-band SMI tooling and telemetry (thermal/power/memory); formulate fault coverage and recovery behaviors for serviceability.
    \item Partner with firmware and silicon teams on compute partitioning, SMI hooks, \textbf{HIP} profiling, and parallel execution models.
    \item Actively contribute to \textbf{Open Source} firmware ecosystem; track architecture defects, enhancements, and issues leveraging the \textbf{Mantis database}.
\end{itemize}

{\textbf{Senior Firmware Development Engineer at Intel Technology India Pvt Ltd}}  \hfill {Oct 2023 - Mar 2024}
\begin{itemize}
    \item Co-architected Universal Scalable Firmware (USF) orchestration layer; aligned \textbf{UEFI Firmware}/\textbf{BMC} configuration flows and lifecycle policies.
    \item Built provisioning pipelines for HPC boards: remote \textbf{BMC}/\textbf{BIOS} flashing, OS deploy, \textbf{EFI}/OS boot automation via \textbf{Redfish} and \textbf{Jenkins}.
    \item Tuned \textbf{boot-time performance}; hardened firmware delivery with staged deploy and artifact signing for notebook platforms.
\end{itemize}
 
{\textbf{Firmware Development Engineer at Intel Technology India Pvt Ltd}}  \hfill {Jun 2020 - Sept 2023}
\begin{itemize}
    \item Led \textbf{UEFI firmware} automation and SDLC compliance: security gates, static analysis, and code quality for the \textbf{EDK2} ecosystem.
    \item Built and maintained full-scale \textbf{firmware} functional validation workflows; owned GitHub review hooks, Jenkins CI, and \textbf{Open Source} compliance tools.
\end{itemize}

{\textbf{Firmware Engineer Intern at Intel Technology India Pvt Ltd}}  \hfill {Jun 2019 - May 2020}
\begin{itemize}
    \item \textbf{BIOS}/\textbf{UEFI} (\textbf{EDK2}) development for client platforms; evaluated hardware debugging solutions and \textbf{OpenBoard} package integration.
\end{itemize}

% \if\profile2
{\textbf{Teaching Assistantship at Nirma University}}  \hfill {Aug 2018 - May 2019}
\begin{itemize}
    \item Data Mining and Visulaization
\end{itemize}
% \fi

% \if\profile1
{\textbf{Software Developer at Quixom Technology}}   \hfill {Jul 2017 - Apr 2018}
\begin{itemize}
    \item SaaS-Employee management system (chat, surveys, benchmark, analytics...) and Restful API Development
    \item Socket programming in python to receive continuous data from IoT device and display chunks of data meaningfully
    \item Streaming service with Web-Portal, DRF and Kodi across platforms
\end{itemize}

{\textbf{Freelance Full-stack Developer}}   \hfill {2015 - Apr 2019}
\begin{itemize}
    \item Cloud solution for Data gathering and webscraping with selenium and GCP.
    \item Designing template and banners for High resolution prints
    \item Inventory management system for Book store with Django.
\end{itemize}
% \fi

\end{rSection}


%----------------------------------------------------------------------------------------
%     PROJECT SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Projects}
{\bf Platform Provisioning with Pre-Production Reference Board} \hfill {2023 - 2024}\\
\textbf{Description}: Automated bring-up for pre-production server processors.

\begin{itemize}
    \item Remote BMC/BIOS flashing and OS deployment from artifactory via Jenkins pipeline.
    \item EFI/OS boot automation and initial setup using Redfish API; reduced manual touch.
\end{itemize}

{\bf Firmware Automation Framework}  \hfill {2020 - Present} \\
\textbf{Description}: SDL-compliant automation for UEFI firmware at scale.

\begin{itemize}
    \item Zero-touch BIOS configuration; security/legal/licensing/static-analysis gates.
    \item Continuous deployment and test with Jenkins/tox; artifact publish to JFrog via GitHub Actions.
    \item \href{https://github.com/intel/xml-cli}{https://github.com/intel/xml-cli}
\end{itemize}

{\bf \textbf{RAS} and Telemetry for \textbf{GPU Firmware}} \hfill {2024 - Present}\\
\textbf{Description}: In-band profiling and \textbf{RAS for GPU firmware with use-case scenario injection} on \textbf{ROCm} stack.

\begin{itemize}
    \item Telemetry for thermal/power/utilization; dynamic workload orchestration from hardware metrics.
    \item Developed reproducible tests and mapped defects using the \textbf{Mantis database} to drive \textbf{Open Source} issue resolution.
\end{itemize}

\textbf{Universal Scalable Firmware} \hfill {2022 - 2024} \\
\textbf{Description}: Platform orchestration layer for \textbf{UEFI firmware} configuration.

\begin{itemize}
    \item Motivation of workgroup - \href{https://uefi.org/sites/default/files/resources/Firmware%20Configuration%20%E2%80%93%20Past,%20Present,%20and%20Future_Zimmer.pdf}{Firmware Configuration – Past, Present, and Future}
    \item \href{https://universalscalablefirmware.github.io/documentation/7_yaml_boot_configuration.html}{Firmware Configuration}
\end{itemize}

{\bf Intelligent Defect Triage System using RAG \& LangGraph (R\&D)} \hfill {2024 - Present}\\
\textbf{Description}: AI-powered defect analysis and real-time triage prediction for enterprise validation workflows.

{\bf Prompt Engineering and Generative AI for firmware stack} \hfill {2023 - 2024}\\
\textbf{Description}: Accelerated \textbf{firmware} deliveries with LLM assistance.

\begin{itemize}
    \item Task summarization via Azure OpenAI (GPT3.5/4); code review guidance vs static-check standards.
    \item Automated code enhancement suggestions for firmware teams.
\end{itemize}

% \textbf{Consummating Research Projects using Agile Manifesto} \hfill {2018}\\
% \textbf{Description}: Utilization of Agile Manifesto for consummating research projects. Enlightening the appropriateness of Scrum for the research projects which is a widely used agile manifesto at present in the software industry.

% \textbf{Inventory Management and GST Billing for Mobile Shop} \hfill {2018}\\
% \textbf{Description}: To avoid the headache of manual billing automated GST billing system designed to manage stocks and update according to purchase and sales and generate GST invoice for sales.

% \textbf{Streaming Box} \hfill {2017 - 2018}\\
% \textbf{Description}: An alternate streaming service to DTH and providing easy customized IPTV streaming service based on Kodi (formerly xbmc) Framework

% \begin{itemize}
%     \item Backend Streaming Service, authentication and server security with Django Framework and REST API
%     \item Web Portal to enable vendor customize Streaming Front-end UI for their users
%     \item Cross compilation and Native compilation to enable various platform support as Android, Windows and MacOS
% \end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf M.Tech Computer Science} \hfill {Jul 2018 - Jun 2020 }
\\ 
Nirma University, GPA: 8.49

{\bf B.E. in Computer Science and Engineering} \hfill {Aug 2013 - Apr 2017 }
Gujarat Technological University, CGPA: 8.08

{\textbf{12th Science, GSHSEB, Class XII}}  \hfill {Jun 2011 - Mar 2013 }\\
Science Stream, 74.92\% 
 
% {\textbf{GSHSEB, Class X}}  \hfill {Jun 2010 - Mar 2011 }\\
% 81.4\%

%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\

\end{rSection}

%----------------------------------------------------------------------------------------
%     Certifications
%----------------------------------------------------------------------------------------
\begin{rSection}{Certifications}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
2025 & \href{https://learning.amd.com/certs/11279/95A05A0CC78443498F47FD0FDB6188FC65062.pdf}{AMD ROCm Star - Application Developer} by AMD Adaptive Computing Training Team
\\
2025 & \href{https://learn.deeplearning.ai/accomplishments/f4188f58-c075-45f4-b2c8-6b6318c51ceb?usp=sharing}{On-Device AI} by Qualcomm \& DeepLearning.ai
\\
2025 & \href{https://www.linkedin.com/learning/certificates/bfa1f8149f171120da54a209a31361de4ac56fe1e3f167e2cbc8cd9fd7ca38d1?u=2140730}{Essential Terraform in AWS}
\\
2021 & \href{https://www.credly.com/badges/a3861155-a2e2-43d5-a8dd-cc21651c5841?source=linked_in_profile}{Product Assurance and Security Yellow Belt - Software}
\\
2020 & Natural Language Processing with Classification
and Vector Spaces
\\ & \href{https://coursera.org/verify/S9DGGMCDMBGQ}{Coursera S9DGGMCDMBGQ}
\\
2020 & Improving Deep Neural Networks: Hyperparameter
Tuning, Regularization and Optimization
\\ & \href{https://coursera.org/verify/SMWQJKJYJW6G}{Coursera SMWQJKJYJW6G}
\\
2020 & Structuring Machine Learning Projects - \href{https://coursera.org/verify/SEJML7H3TN5Z}{Coursera SEJML7H3TN5Z}
\\
2020 & Neural Networks and Deep Learning - \href{https://coursera.org/verify/S2TETZHTLUSL}{Coursera S2TETZHTLUSL}
\\
2020 & Machine Learning - \href{https://coursera.org/verify/XVNXNPPZ3JMA}{Coursera XVNXNPPZ3JMA}

\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%     Achievements
%----------------------------------------------------------------------------------------
\begin{rSection}{Achievements}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
2023 & Firmware Configuration Presentation at UEFI Developers Conference \& Plugfest \\
2023 & Tech Talk on Harnessing Multiprogramming across CPU, GPU and 
\\ & QPU (Quantum Processing Unit) \\
2021 & Expert Lecture on CUDA Programming \\
2019-Present & 4000+ reputation on Stackoverflow \\
2017-Present & Active volunteer on Peer Learning, Cultural and team building activity \\
2018 & Rank \#1 for Python challenges on hackerrank \\
2018 & Rank \#112 from 2 lacs+ participants in Techgig's National Coding Contest 2018 \\
% 2014 & Establishment of complete network for Department

\end{tabular}

\end{rSection}
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%     Publications
%----------------------------------------------------------------------------------------
\begin{rSection}{Publications}

\begin{itemize}
    \item \href{https://youtube.com/playlist?list=PLWyBQeJgIuzDFELUK9ineNkOr9LuYatkR&si=mUVeIkLFK5gzyZa7}{HIP Parallel Programming with ROCm} Lecture Series, YouTube  \hfill {2025}
    \item \href{https://youtube.com/playlist?list=PLWyBQeJgIuzC6oN8AihmSMkgheX9TLDaW&si=HAOmHXKP4KdsAzPX}{Beyond the Power | Data Center \& BMC} Lecture Series, YouTube  \hfill {2025}
    \item \href{https://www.youtube.com/playlist?list=PLWyBQeJgIuzD2o9ZVw5oI-P2fX4uyNKZA}{System Design for Parallel Programming} Lecture Series, YouTube  \hfill {2025}
    % \item A Review on Honeypot : Track the Attack. NCCICT, 2016 \hfill {2016}
    \item \href{https://uefi.org/sites/default/files/resources/Firmware%20Configuration%20%E2%80%93%20Past%2C%20Present%2C%20and%20Future_Zimmer.pdf}{Firmware Configuration – Past, Present, and Future}. Presentation, UEFI DevCon 2023 \hfill {2023}
\end{itemize}


\end{rSection}

\end{document}

