%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\usepackage{fontawesome}
\usepackage{setspace}
\usepackage{hyperref}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Gahan Saraiya} % Your name
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{ 
  \faPhone \ +91 7359508173 \\
  \faEnvelope \ \href{mailto: gahansaraiya@gmail.com}{gahansaraiya@gmail.com} \\  
  \faLinkedin \ \href{https://www.linkedin.com/in/gahan-saraiya/}{linkedin.com/in/gahan-saraiya} \\ \faGithub \   \href{https://github.com/gahan9/}{github.com/gahan9} 
}  % Your phone number and email

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
    pdfpagemode=FullScreen,
    }
\begin{document}

% AI/ML - 0
% DevOps - 1
% PhD - 2
\def\profile{0}

%----------------------------------------------------------------------------------------
%	PROFESSIONAL SUMMARY
%----------------------------------------------------------------------------------------

\begin{rSection}{PROFESSIONAL SUMMARY}
{Staff-level Software Engineer with 8+ years of expertise in High-Performance Computing (HPC), parallel programming, and distributed systems architecture. Proven track record in designing and implementing scalable cluster architectures, health telemetry systems, and GPU-accelerated workloads for data center environments. Specialized in System Management Interface (SMI) design, workload orchestration, and performance optimization across heterogeneous computing platforms. Led cross-functional teams in developing enterprise-grade firmware automation frameworks and platform provisioning systems. Strong background in CUDA, ROCm, HIP programming, and cloud-native infrastructure.}

\end{rSection}




%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{TECHNICAL SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{1ex}} l }

% PROFILE 0
\if\profile0
Programming Languages & \textbf{Python}, C, \textbf{C++}, \textbf{CUDA}, \textbf{HIP}, Shell Scripting, SQL, YAML, LaTeX
\\
Parallel \& Distributed Computing & CUDA Programming, ROCm, \textbf{HIP Programming}, Multi-GPU Systems, 
\\ & Cluster Architecture Design, Workload Orchestration, 
\\ & Parallel Algorithm Design
\\
Health Telemetry \& Monitoring & System Management Interface (SMI), GPU Telemetry,
\\ & Hardware Metrics, Performance Profiling, In-Band Monitoring, 
\\ & Real-time Health Monitoring
\\
ML/AI Frameworks & TensorFlow, PyTorch, TensorRT, PyCUDA, Pandas, NumPy, GEMM
\\
System Software \& Firmware & UEFI, EDK2, Firmware Architecture, Boot Optimization, \textbf{RAS} (
\\ & Reliability, Availability, Serviceability), CPER, GPU Partitioning
\\
DevOps \& Infrastructure & Kubernetes, Docker, Docker Compose, Terraform, Jenkins, GitHub Actions,
\\ & CI/CD Pipelines, Infrastructure as Code, Platform Provisioning
\\
Cloud \& Services & AWS (EC2, S3, Lambda, SageMaker, ECS, EKS), GCP, Azure,
\\ & RESTful APIs, JFrog Artifactory, TeamCity, JIRA
\\
\fi

%  PROFILE 1
\if\profile1
Languages & Python, Shell Scripting, SQL, LaTeX, YAML 
\\
Frameworks & Pytorch, Pytest, Edk2, PyCUDA, Pandas, UEFI, Selenium, Redfish
\\
Architecture Design & Parallel Programming System Architecture, ROCm, HIP Programming
\\
Tools and Services & GitHub Actions, Jenkins, Restful APIs, Teamcity, Terraform,
\\ & Docker, Docker Compose, Jenkins, TeamCity, GiT 
\\
Cloud Technologies & AWS EC2, AWS S3, AWS Cloudwatch, VPC Networking, AWS Sage Maker, 
\\ & AWS Lambda, AWS Cloudfront, ECR, ECS, EKS, JFrog Artifactory
\\ & GCP, Azure, Digital Ocean
    
\fi

\end{tabular}

\end{rSection}


%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	Experience SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

{\bf Senior System Software Designer at AMD India Pvt Ltd} \hfill {Mar 2024 - Present }
\begin{itemize}
    \item Architected and implemented in-band health telemetry system for GPU clusters using System Management Interface (SMI), enabling real-time monitoring of temperature, power consumption, memory utilization, and compute core metrics across data center deployments.
    \item Designed and developed dynamic workload orchestration framework for multi-GPU cluster environments, implementing load balancing algorithms that optimize resource allocation based on real-time hardware telemetry and thermal constraints.
    \item Led performance benchmarking initiatives for HPC devices (GPUs), developing comprehensive test suites covering TensorFlow, PyTorch, and GEMM operations that validate performance against industry standards and identify optimization opportunities.
    \item Architected parallel programming solutions using ROCm and HIP frameworks, enabling efficient multi-GPU workload distribution and achieving improved cluster utilization through intelligent workload scheduling.
    \item Designed and implemented RAS (Reliability, Availability, Serviceability) injection mechanisms for MI2XX and MI3XX platforms, establishing health monitoring protocols and automated recovery procedures for production environments.
    \item Developed cluster health monitoring infrastructure with in-band profiling capabilities, capturing kernel-level performance metrics and system telemetry to enable proactive issue detection and performance optimization.
    \item Collaborated with cross-functional teams of engineers and researchers to define system architecture requirements, establish best practices for parallel programming, and drive technical decisions for next-generation HPC platforms.
\end{itemize}

{\textbf{Senior Firmware Development Engineer at Intel Technology India Pvt Ltd}}  \hfill {Oct 2023 - Mar 2024}
\begin{itemize}
    \item Architected platform provisioning infrastructure for large-scale HPC product automation, designing cluster-based deployment systems that reduced manual configuration time by 70\% through automated provisioning workflows.
    \item Led Platform Orchestration Layer (POL) architecture design for Universal Scalable Firmware (USF), establishing scalable firmware configuration management framework supporting heterogeneous computing platforms.
    \item Designed and implemented Terraform-based infrastructure automation for Kubernetes cluster environments, enabling rapid deployment of development and testing platforms with infrastructure-as-code practices.
    \item Integrated Azure OpenAI services into firmware development workflow, implementing automated code review, security analysis, and enhancement suggestions that accelerated development cycles.
    \item Architected CI/CD pipeline infrastructure using GitHub Actions and CloudBees Jenkins, supporting both bare-metal and containerized deployment targets for continuous integration and testing.
    \item Optimized firmware boot-time performance for client platforms, implementing parallel initialization strategies that reduced boot latency by 15\%.
\end{itemize}
 
{\textbf{Firmware Development Engineer at Intel Technology India Pvt Ltd}}  \hfill {Jun 2020 - Sept 2023}
\begin{itemize}
    \item Led architecture design for next-generation client platform at USF Platform Orchestration Layer, owning domain responsibilities for Automation Framework, Platform Provisioning, and Generative AI integration for firmware development.
    \item Managed end-to-end Software Development Lifecycle (SDLC) including licensing, legal compliance, IP planning, code security, and static code analysis, establishing processes that ensured compliance across all firmware releases.
    \item Architected and implemented automated security scanning infrastructure using Jenkins, integrating Snyk and Coverity for continuous security analysis and vulnerability detection in firmware codebase.
    \item Developed automated code quality pipeline using GitHub hooks, implementing Python packaging validation, linting with Bandit, and security analysis that improved code quality metrics by 40\%.
    \item Designed and implemented automated firmware validation framework using TeamCity, enabling continuous functional testing and reducing manual testing overhead by 60\%.
    \item Mentored junior engineers and conducted technical knowledge-sharing sessions on firmware architecture, parallel programming concepts, and system design principles.
\end{itemize}

{\textbf{Firmware Engineer Intern at Intel Technology India Pvt Ltd}}  \hfill {Jun 2019 - May 2020}
\begin{itemize}
    \item Developed BIOS firmware for client products using EDK2 and UEFI frameworks, contributing to debugging solutions and OpenBoard Package integration.
\end{itemize}

\end{rSection}


%----------------------------------------------------------------------------------------
%     PROJECT SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Projects}
{\bf GPU Cluster Performance Analysis \& Health Telemetry System} \hfill {2024 - Present}\\
\textbf{Description}: Enterprise-grade solution for in-band profiling and health monitoring of GPU clusters in data center environments

\begin{itemize}
    \item \textbf{Cluster Health Telemetry Architecture:} Architected and implemented comprehensive in-band profiling system using System Management Interface (SMI) for real-time GPU cluster health monitoring, capturing telemetry data across temperature, power, memory, and compute utilization metrics.
    \item \textbf{Dynamic Cluster Workload Orchestration:} Designed intelligent workload scheduling system that dynamically adapts to real-time cluster resource availability, implementing load balancing algorithms that optimize multi-GPU workload distribution and improve overall cluster efficiency.
    \item \textbf{Distributed Health Monitoring Infrastructure:} Engineered scalable telemetry collection framework supporting hundreds of GPU nodes, implementing in-band monitoring channels that minimize performance overhead while providing comprehensive hardware metric visibility.
    \item \textbf{Performance Profiling \& Analysis:} Developed advanced profiling infrastructure capturing kernel-level performance metrics, call stack timings, and execution patterns to identify bottlenecks and optimize parallel program performance across cluster deployments.
    \item \textbf{Unified Analytics Platform:} Innovated methodology to aggregate and correlate multi-dimensional metrics (thermal, power, utilization, kernel timings) into unified health scores, enabling predictive maintenance and proactive cluster management.
\end{itemize}

\textbf{Platform Orchestration \& Cluster Provisioning System} \hfill {2023 - 2024}\\
\textbf{Description}: Automated platform provisioning infrastructure for large-scale HPC cluster deployment

\begin{itemize}
    \item Architected cluster provisioning framework supporting remote BMC and BIOS firmware flashing across distributed server nodes, enabling zero-touch deployment for pre-production reference boards.
    \item Designed automated OS deployment pipeline integrated with Jenkins, supporting artifact management through JFrog Artifactory and RedFish API-based system configuration.
    \item Implemented infrastructure-as-code practices using Terraform for cluster environment provisioning, reducing deployment time from days to hours.
\end{itemize}

\textbf{Universal Scalable Firmware (USF) - Platform Orchestration Layer} \hfill {2022 - 2024} \\
\textbf{Description}: Architecture design of scalable firmware configuration management for heterogeneous computing platforms

\begin{itemize}
    \item Led architecture design of Platform Orchestration Layer enabling unified firmware configuration across diverse hardware platforms, contributing to UEFI industry standard development.
    \item Reference: \href{https://uefi.org/sites/default/files/resources/Firmware%20Configuration%20%E2%80%93%20Past%2C%20Present%2C%20and%20Future_Zimmer.pdf}{Firmware Configuration – Past, Present, and Future} (UEFI DevCon 2023)
\end{itemize}

\textbf{Firmware Automation Framework}  \hfill {2020 - Present} \\
\textbf{Description}: Enterprise automation framework for large-scale firmware development and validation

\begin{itemize}
    \item Architected end-to-end automation framework supporting thousands of silicon devices, implementing zero-touch BIOS configuration and automated validation workflows.
    \item Established SDLC processes including security scanning, static code analysis, legal compliance, and licensing management integrated into CI/CD pipelines.
    \item Designed continuous deployment infrastructure using Jenkins and GitHub Actions, managing release artifacts through JFrog Artifactory with automated testing and validation.
    \item Open Source: \href{https://github.com/intel/xml-cli}{https://github.com/intel/xml-cli}
\end{itemize}

% \textbf{Consummating Research Projects using Agile Manifesto} \hfill {2018}\\
% \textbf{Description}: Utilization of Agile Manifesto for consummating research projects. Enlightening the appropriateness of Scrum for the research projects which is a widely used agile manifesto at present in the software industry.

% \textbf{Inventory Management and GST Billing for Mobile Shop} \hfill {2018}\\
% \textbf{Description}: To avoid the headache of manual billing automated GST billing system designed to manage stocks and update according to purchase and sales and generate GST invoice for sales.

% \textbf{Streaming Box} \hfill {2017 - 2018}\\
% \textbf{Description}: An alternate streaming service to DTH and providing easy customized IPTV streaming service based on Kodi (formerly xbmc) Framework

% \begin{itemize}
%     \item Backend Streaming Service, authentication and server security with Django Framework and REST API
%     \item Web Portal to enable vendor customize Streaming Front-end UI for their users
%     \item Cross compilation and Native compilation to enable various platform support as Android, Windows and MacOS
% \end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf M.Tech Computer Science} \hfill {Jul 2018 - Jun 2020 }
\\ 
Nirma University, GPA: 8.49

{\bf B.E. in Computer Science and Engineering} \hfill {Aug 2013 - Apr 2017 }
Gujarat Technological University, CGPA: 8.08

%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\

\end{rSection}

%----------------------------------------------------------------------------------------
%     Certifications
%----------------------------------------------------------------------------------------
\begin{rSection}{Certifications}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
2025 & \href{https://learning.amd.com/certs/11279/95A05A0CC78443498F47FD0FDB6188FC65062.pdf}{AMD ROCm Star - Application Developer} by AMD Adaptive Computing Training Team
\\
2025 & \href{https://learn.deeplearning.ai/accomplishments/f4188f58-c075-45f4-b2c8-6b6318c51ceb?usp=sharing}{On-Device AI} by Qualcomm \& DeepLearning.ai
\\
2025 & \href{https://www.linkedin.com/learning/certificates/bfa1f8149f171120da54a209a31361de4ac56fe1e3f167e2cbc8cd9fd7ca38d1?u=2140730}{Essential Terraform in AWS}
\\
2021 & \href{https://www.credly.com/badges/a3861155-a2e2-43d5-a8dd-cc21651c5841?source=linked_in_profile}{Product Assurance and Security Yellow Belt - Software}
\\
2020 & Natural Language Processing with Classification
and Vector Spaces
\\ & \href{https://coursera.org/verify/S9DGGMCDMBGQ}{Coursera S9DGGMCDMBGQ}
\\
2020 & Improving Deep Neural Networks: Hyperparameter
Tuning, Regularization and Optimization
\\ & \href{https://coursera.org/verify/SMWQJKJYJW6G}{Coursera SMWQJKJYJW6G}
\\
2020 & Structuring Machine Learning Projects - \href{https://coursera.org/verify/SEJML7H3TN5Z}{Coursera SEJML7H3TN5Z}
\\
2020 & Neural Networks and Deep Learning - \href{https://coursera.org/verify/S2TETZHTLUSL}{Coursera S2TETZHTLUSL}
\\
2020 & Machine Learning - \href{https://coursera.org/verify/XVNXNPPZ3JMA}{Coursera XVNXNPPZ3JMA}

\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%     Achievements
%----------------------------------------------------------------------------------------
\begin{rSection}{Achievements}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
2023 & Firmware Configuration Presentation at UEFI Developers Conference \& Plugfest \\
2023 & Tech Talk on Harnessing Multiprogramming across CPU, GPU and 
\\ & QPU (Quantum Processing Unit) \\
2021 & Expert Lecture on CUDA Programming \\
2019-Present & 4000+ reputation on Stackoverflow \\
2017-Present & Active volunteer on Peer Learning, Cultural and team building activity \\
2018 & Rank \#1 for Python challenges on hackerrank \\
2018 & Rank \#112 from 2 lacs+ participants in Techgig's National Coding Contest 2018 \\
% 2014 & Establishment of complete network for Department

\end{tabular}

\end{rSection}
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%     Publications
%----------------------------------------------------------------------------------------
\begin{rSection}{Publications}

\begin{itemize}
    \item \href{https://youtube.com/playlist?list=PLWyBQeJgIuzDFELUK9ineNkOr9LuYatkR&si=mUVeIkLFK5gzyZa7}{HIP Parallel Programming with ROCm} Lecture Series, YouTube  \hfill {2025}
    \item \href{https://youtube.com/playlist?list=PLWyBQeJgIuzC6oN8AihmSMkgheX9TLDaW&si=HAOmHXKP4KdsAzPX}{Beyond the Power | Data Center \& BMC} Lecture Series, YouTube  \hfill {2025}
    \item \href{https://www.youtube.com/playlist?list=PLWyBQeJgIuzD2o9ZVw5oI-P2fX4uyNKZA}{System Design for Parallel Programming} Lecture Series, YouTube  \hfill {2025}
    % \item A Review on Honeypot : Track the Attack. NCCICT, 2016 \hfill {2016}
    \item \href{https://uefi.org/sites/default/files/resources/Firmware%20Configuration%20%E2%80%93%20Past%2C%20Present%2C%20and%20Future_Zimmer.pdf}{Firmware Configuration – Past, Present, and Future}. Presentation, UEFI DevCon 2023 \hfill {2023}
\end{itemize}


\end{rSection}

\end{document}

